A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-10-04 sections/healthcare_application/main.tex
Methodology section (#15)
* Remove TODOs that were addressed

* Minor changes to other sections

* Write intro for methodology section

* Fix minor bibliography issue

* Minor change in some of the mathematics

* Write Backwards Induction subsection

* Changes to Methodology and Model overview sections

- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings

* Move asymmetric replicator dynamics to methodology

Move from ED-EMS appllication section to Methodology section

* Add Nash

The most commonly used method for analysing normal form games is the Nash 
equilibrium \cite{kreps1989nash}. 
The Nash equilibrium is the point of the game were players have no incentive to 
deviate from their strategy.
Consider the following game:

>>>>

The most commonly used method for analysing normal form games is the Nash 
equilibrium described in section \ref{sec:methodology_nash_equilibrium}
Consider the following game:

### 2021-10-04 sections/model_overview/main.tex
Methodology section (#15)
* Remove TODOs that were addressed

* Minor changes to other sections

* Write intro for methodology section

* Fix minor bibliography issue

* Minor change in some of the mathematics

* Write Backwards Induction subsection

* Changes to Methodology and Model overview sections

- Chnages in some notation
- Define expressions only once and then just reference them
- Changes in some labels (including some more sections)
- Other minor rewordings

* Move asymmetric replicator dynamics to methodology

Move from ED-EMS appllication section to Methodology section

* Add Nash

This is a standard Normal form game~\cite{Maschler2013},  
in that each player in this game has their own objectives which they aim to 
optimise.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.
% TODO: Depending on how this is described earlier, we might need a little more 
% here (as to what we mean by "blocked")

@@

\begin{equation}
    P(W < R) \geq \hat{P}
\end{equation}

where \(W\) is the mean waiting time of all individuals, \(R\) is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
For example one approach is to use the threshold that maximises the probability 
that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal.

\begin{equation}
    \arg \max_{T_i} \quad P(W_i < R)
\end{equation}

@@

\begin{equation}\label{eq:obj-queueing-systems}
    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < R) \right)^2
\end{equation}

The third player, the distributor has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p \leq 1\) of 
individuals it sends to the first queueing system (the proportion \(1 - q\) is 
sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals 
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals.
Equation \ref{eq:obj_distributor} can be used to capture a mixture 
between the two objectives.

\begin{equation}\label{eq:obj_distributor}
    \alpha P(L_A) + (1 - \alpha) B_A = 
    \alpha P(L_B) + (1 - \alpha) B_B
\end{equation}

@@

Using equations \ref{eq:obj-queueing-systems} and \ref{eq:obj_distributor} gives
an imperfect information extensive form game. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players~\cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without the 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked. Figure \ref{fig:imperfect-info-game} illustrates this.

@@

        \path[->] (D) edge node {}(D_d1);
        \path[->] (D) edge node {}(D_d2);
        \path(D_d1) edge [bend left] node {}(D_d2);
    \end{tikzpicture}
    \caption{Imperfect information Extensive Form Game between the distributor 
    and the 2 queueing systems}
    \label{fig:imperfect-info-game}
\end{figure}

@@

In order to define the normal form game the two payoff matrices of the players 
are required. From equation \ref{eq:obj-queueing-systems} the utilities of the
players can be formulated as:

\begin{equation} \label{eq:payoff-entry}
    U_{T_1, T_2}^i = \quad -\left( 
        \hat{P} - P(W_i < R) 
    \right)^2
\end{equation}

@@

\begin{equation} \label{eq:payoff_matrices}
    A = 
    \begin{pmatrix}
        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
    \end{pmatrix},
    B = 
    \begin{pmatrix}
        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
    \end{pmatrix}
\end{equation}

>>>>

This is a standard normal form game~\cite{Maschler2013},  
in that each player in this game has their own objectives which they aim to 
optimise.
More specifically, the queueing systems' objective is captured by an upper bound
of the time that a fixed proportion of individuals spend in the system, 
while the distributor aims to minimise the time that its individuals 
are blocked.
% TODO: Depending on how this is described earlier, we might need a little more 
% here (as to what we mean by "blocked")

@@

\begin{equation}
    P(W < t) \geq \hat{P}
\end{equation}

where \(W\) is the mean waiting time of all individuals, \(t\) is the time 
target and \(\hat{P}\) is the percentage of individuals need to be within that 
target. 
There are numerous objective functions that can be used to capture this 
behaviour. 
For example one approach is to use the threshold that maximises the probability 
that 
the mean waiting is more than the target time, and completely ignore the 
percentage goal.

\begin{equation}
    \arg \max_{T_i} \quad P(W_i < t)
\end{equation}

@@

\begin{equation}\label{eq:obj_queueing_systems}
    \arg \max_{T_i} \quad -\left( \hat{P} - P(W_i < t) \right)^2
\end{equation}

The third player, the distributor has their own choices to make and their own 
goals to satisfy.
The strategy set of the third player is the proportion \(0 \leq p_A \leq 1\) of 
individuals it sends to the first queueing system (the proportion 
\(p_B = 1 - p_A\) is sent to the second queueing system).
In addition, the distributor aims to minimise any potential blockages
that may occur, given the pair of thresholds chosen by the two queueing systems.
Thus, its objective is to minimise the blocked time of the individuals (\(B_i\))
that they send to the two queueing systems.
Apart from the time being blocked, an additional aspect that may affect the 
decision of the distributor is the proportion of lost individuals (\(L_i\)).
Equation \ref{eq:obj_distributor} can be used to capture a mixture 
between the two objectives \(L_i\) and \(B_i\) where \(i \in \{A, B\}\).
\begin{equation*}\label{eq:obj_distributor}
    (p_A, p_B) \quad s.t. \quad 
    \alpha L_A(p_A) + (1 - \alpha) B_A(p_A) = 
    \alpha L_B(p_B) + (1 - \alpha) B_B(p_B)
\end{equation*}

@@

Using equations (\ref{eq:obj_queueing_systems}) and (\ref{eq:obj_distributor}) 
gives an imperfect information extensive form game. 
An imperfect information game is defined as an extensive form game where some 
of the information about the game state is hidden for at least one of the 
players~\cite{Berwanger2008}. In this study the state of the problem that is
hidden is the threshold that each of the first two players chooses to play.
In other words, each queueing system chooses to play a strategy without 
knowing the other system's strategy.
The distributor then, fully aware of the chosen threshold strategies, distributes 
individuals among the two systems in order to minimise the time that its 
individuals will be blocked. Figure \ref{fig:imperfect_info_game} illustrates this.

@@

        \path[->] (D) edge node {}(D_d1);
        \path[->] (D) edge node {}(D_d2);
        \path(D_d1) edge [bend left] node {}(D_d2);
    \end{tikzpicture}
    \caption{Imperfect information Extensive Form Game between the distributor 
    and the 2 queueing systems}
    \label{fig:imperfect_info_game}
\end{figure}

@@

In order to define the normal form game the two payoff matrices of the players 
are required. From equation \ref{eq:obj_queueing_systems} the utilities of the
players can be formulated as:

\begin{equation} \label{eq:payoff_entry}
    U_{T_1, T_2}^i = -\left( 
        \hat{P} - P(W_i < t) 
    \right)^2 \quad \textbf{where } i \in \{A, B\}
\end{equation}

@@

\begin{equation} \label{eq:payoff_matrices}
    A = 
    \begin{pmatrix}
        U_{1,1}^A & U_{1,2}^A & \dots & U_{1,N_B}^A \\
        U_{2,1}^A & U_{2,2}^A & \dots & U_{2,N_B}^A \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^A & U_{N_A,2}^A & \dots & U_{N_A,N_B}^A \\
    \end{pmatrix}, \,
    B = 
    \begin{pmatrix}
        U_{1,1}^B & U_{1,2}^B & \dots & U_{1,N_B}^B \\
        U_{2,1}^B & U_{2,2}^B & \dots & U_{2,N_B}^B \\
        \vdots & \vdots & \ddots & \vdots \\
        U_{N_A,1}^B & U_{N_A,2}^B & \dots & U_{N_A,N_B}^B \\
    \end{pmatrix}
\end{equation}
